Appendix B: Examples of Deep RL in Ecological Decision Problems

### 2021-05-20 appendices/appendix-B-examples.Rmd
update paths

write_csv(sims_df, "figs/sims_df.csv")
write_csv(policy_df, "figs/policy_df.csv")
write_csv(reward_df, "figs/reward_df.csv")
```

@@

```{r message=FALSE, fig.cap="Bifurcation diagram for tipping point scenario. The ecosystem begins in the desirable 'high' state under an evironmental parameter (e.g. global mean temperature, arbitrary units) of 0.19.  In the absence of conservation action, the environment worsens (e.g. rising mean temperature) as the parameter increases.  This results in only a slow degredation of the stable state, until the parameter crosses the tipping point threshold at about 0.215, where the upper stable branch is anihilated in a fold bifurcation and the system rapidly transitions to lower stable branch, around state of 0.1.   Recovery to the upper branch requires a much greater conservation investment, reducing the parameter all the way to 0.165 where the reverse bifurcation will carry it back to the upper stable branch."}
bifur_df = read_csv("figs/bifur.csv", col_types = "dccd")
bifur_df %>%
  ggplot(aes(parameter, state, lty=equilibrium, group = group)) + 
  geom_line()

@@

```{r}
write_csv(sims_df, "figs/tipping_sims_df.csv")
write_csv(policy_df, "figs/tipping_policy_df.csv")
write_csv(reward_df, "figs/tipping_reward_df.csv")
```

>>>>

write_csv(sims_df, "../manuscript/figs/sims_df.csv")
write_csv(policy_df, "../manuscript/figs/policy_df.csv")
write_csv(reward_df, "../manuscript/figs/reward_df.csv")
```

@@

```{r message=FALSE, fig.cap="Bifurcation diagram for tipping point scenario. The ecosystem begins in the desirable 'high' state under an evironmental parameter (e.g. global mean temperature, arbitrary units) of 0.19.  In the absence of conservation action, the environment worsens (e.g. rising mean temperature) as the parameter increases.  This results in only a slow degredation of the stable state, until the parameter crosses the tipping point threshold at about 0.215, where the upper stable branch is anihilated in a fold bifurcation and the system rapidly transitions to lower stable branch, around state of 0.1.   Recovery to the upper branch requires a much greater conservation investment, reducing the parameter all the way to 0.165 where the reverse bifurcation will carry it back to the upper stable branch."}
bifur_df = read_csv("../manuscript/figs/bifur.csv", col_types = "dccd")
bifur_df %>%
  ggplot(aes(parameter, state, lty=equilibrium, group = group)) + 
  geom_line()

@@

```{r}
write_csv(sims_df, "../manuscript/figs/tipping_sims_df.csv")
write_csv(policy_df, "../manuscript/figs/tipping_policy_df.csv")
write_csv(reward_df, "../manuscript/figs/tipping_reward_df.csv")
```
